\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Introduction}

\subsection{Overview}
TimeStrike is an accessible miniatures wargame built as a Boss Battle Royale. Players will take turns managing a team of Characters by moving them around the Void and performing actions in an attempt to be the last team standing. 

\subsubsection{Lore}
Universes collide as characters from ancient civilizations and distant futures reach the end of time. It is here that history ends, and your adventure begins. A malignant Sentience has pulled you into the timescape, a land of decaying universes, creating a rift in time. You must assemble a team, scavenge for loot, mine for materials, complete quests, build defenses, and fight for control of the Sentience, harnessing its massively destructive abilities to be the last team standing to control the Sentience and escape! At its core, TimeStrike is a game about the enduring, adaptable, and fierce nature of the human spirit. It’s a game about managing relationships, resources, and the environment itself to overcome adversity against all odds. At the end of time, you may be down, but you’re never out.

\subsection{Important Notes}
TimeStrike is a scalable game. The Shadow of Fear box comes with everything needed for games of up to 3 players, but multiple sets of TimeStrike can be combined to accommodate groups of any size.
Most rule exceptions are found on cards. If during gameplay, a contradiction to the rules is encountered, refer to the card first and the rulebook second.

\subsection{Community Outreach}
\subsubsection{Discord}
The Adventure Together community is on Discord. We have a channels specifically for ruleset clarifications and we would love to help!  We will do our best to get you back to Adventuring Together as soon as possible. If you want to have debates about rules or just show off incredible game outcomes and we would also love to see or hear it!
\subsubsection{}
Visit us anytime on Discord: 
https://discord.gg/adventuretogether
\newpage
\subsection{Video Tutorial}
In the next few days we will upload a link here showing a quick video overviewing the TimeStrike mechanics. 

\subsubsection{}
Full Play-Throughs and Tutorials on YouTube: 
https://www.youtube.com/@adventuretogethergames

\clearpage
\end{document}
