\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Player Turns}
During each round, each player takes one turn following these steps: 
\begin{enumerate}
    \item The player chooses one ready (non-exhausted) Survivor Character on their team to take a turn with. (\textit{See the rules for Exhaustion in the next section.}
    \item During a Character's turn, its controller may activate each unit belonging to that Character and each Monster that Character has tamed. 
    \item If  unit has unused Movement or Energy remaining after being activated, it maybe activated again later during the same turn (as long as it has not performed an Attack Action). 
    \item After a player has finished their Character's turn, they must exhaust the Character. 
\end{enumerate}

When activating each unit, the player can use that unit's Movement and Energy stats to move them around the board and perform Actions. A unit may use any amount of its Movement and Energy in any order, but after performing an Attack Action, that unit may no longer use any more of its Movement or Energy and it cannot be activated again during that turn. 

\textit{Note: Units belonging to a multi-unit Character are each activated individually and can each use their full Movement and Energy stats listed on their Character card. }

\subsection{Exhaustion}
After taking a turn with a Character, exhaust that Character by removing the marker from their Exhaustion slot. 

Players will have to keep taking turns with different Characters on their team that aren't exhausted until all their Characters are exhausted. When all the Characters on a team are exhausted, all of the Exhaustion slots are refilled, and the player can then use their Characters in any order again. 

\clearpage

\end{document}