\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Myth}

The Myth mechanic allows players who have been defeated to continue to play the game and seek revenge on those who may have wronged them during the game. A player can only become a Myth if their team is defeated before the Sentience is.

\textit{Note: There are no limits to how many players can become Myths.}

\subsection{TimeStrike Rule Changes}
Once the first Myth is active: 
\begin{enumerate}
    \item All units currently on the Sentience are knocked off and must be placed on unoccupied hexes adjacent to it in turn order.
    \item Players can no longer Tame Monsters or Climb on the Sentience. Loot that tames Monsters or allows the players to climb the Sentience can no longer be used.
    \item Monsters now interact normally with Cheap Shots, rolling Defense, buffs, curses, and the exhaustion system. Treat them as if they were a normal team.
    \item If there are no Lost Monsters available on the board, the Myth can choose one to bring in and place it anywhere on the board.
\end{enumerate}

\subsection{How to Play the Myth Role}
The Myth’s goal is to use the Lost to keep any remaining players from winning. Below are the steps the Myth will take.
\begin{enumerate}
    \item When a player becomes a Myth, they take control of all Lost Monsters on the board to create their own team.
    \item Myth(s) continue to take their turns in normal turn order as they did when they were players but get to choose one of their Monsters to activate for that turn.
    \item During the Myth(s) turn, they can use a Monster of their choice to move and perform the Cast, Contest, and Attack Actions to defeat the remaining players. Other actions like Mining, Trading, and Fishing cannot be performed.
    \item At the end of each round when a card is drawn from the Sentience deck, Myths will have control of the Sentience cards. If there are multiple Myth(s) they will roll against each other to determine who will resolve the Sentience card actions.
\end{enumerate}

\textit{Note: Myth(s) Characters are not able to equip artifacts or store goods in their inventory.}

\clearpage
\end{document}